Demystifying Votes: A Hierarchical Bayesian Model for Predicting the 2024 US Presidential Election

### 2024-11-01 paper/paper.qmd
fig-caps added

```{r, fig.width=5, fig.height=3}
#| echo: false
#| eval: true
#| label: fig-post4
#| fig-cap: "TODO"
#| warning: false

@@

```{r, fig.width=5, fig.height=3}
#| echo: false
#| eval: true
#| label: fig-post5
#| fig-cap: "TODO"
#| warning: false

>>>>

```{r, fig.width=5, fig.height=3}
#| echo: false
#| eval: true
#| label: fig-post4
#| fig-cap: R hat Diagnostic statistic for model
#| warning: false

@@

```{r, fig.width=5, fig.height=3}
#| echo: false
#| eval: true
#| label: fig-post5
#| fig-cap: posterior distributions of four parameters in model
#| warning: false
